COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd

@@

  levelindex <- c(1,which(data_RT$level != dplyr::lag(data_RT$level)),nrow(data_RT))

    # set the number of targets and non-targets
    num_targets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
    num_nontargets <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))

    hits <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
    falsealarms <- length(which(data_RT$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0 &
                           data_RT$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
    newdata <- data.frame(subject = data_RT$subject[levelindex[i]],
                          level = data_RT$level[levelindex[i]],
                          hitrate = hits/num_targets,
                          falsealarmrate = falsealarms/num_nontargets)
    dprime <- rbind(dprime, newdata)

>>>>

```{r pipelines_dprime, echo=FALSE, message=FALSE, warning=FALSE}

  # calculate d' for every pipeline because it depends on the total number of target and non-target trials

  for (j in 1:length(pipelines_data)) {

    levelindex <- c(1,which(pipelines_data[[j]]$level != dplyr::lag(pipelines_data[[j]]$level)),nrow(pipelines_data[[j]]))

      # set the number of targets and non-targets
      num_targets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1))
      num_nontargets <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 0))

      hits <- length(which(pipelines_data[[j]]$target[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 1) + (levelindex[i]-1))
      falsealarms <- length(which(pipelines_data[[j]]$response[c(levelindex[i]:(levelindex[i+1])-1)] == 1 &
                             pipelines_data[[j]]$correct[c(levelindex[i]:(levelindex[i+1])-1)] == 0) + (levelindex[i]-1))
      newdata <- data.frame(subject = pipelines_data[[j]]$subject[levelindex[i]],
                            level = pipelines_data[[j]]$level[levelindex[i]],
                            hitrate = hits/num_targets,
                            falsealarmrate = falsealarms/num_nontargets)
      dprime <- rbind(dprime, newdata)

    # feed d# trialwise into the pipeline data frame

    for (i in 1:nrow(pipelines_data[[j]])) {

      pipelines_data[[j]]$dprime[i] <- dprime$d[dprime$subject == pipelines_data[[j]]$subject[i] & dprime$level == pipelines_data[[j]]$level[i]]

    }
  }

@@
